FEM Model Analysis

### 2021-02-08 FEM_R/model_analysis.Rmd
Added ageUK validation to model_analysis.Rmd and changed the size of the images being saved

# FEM 2014 summary
FEM <- read_dta('ELSA_Baseline/ELSA_Baseline_summary.dta')

@@

  # Save plot into in E-FEM_Paper/figures/
  ggsave(filename = paste0(cd, '_', gender, '.png'),
         plot = p,
         path = path,
         width = 7,
         height = 5)

  p
}

# Collect all conditions (and both genders) into a list, and apply the function above to that list
cd_list <- unique(combined$Condition)
gender_list <- unique(combined$Gender)

for(cd in cd_list) {
  for(gen in gender_list) {
    visAgeUKValid(combined, cd, gen)
  }
}

@@

>>>>

# FEM 2014 summary
#FEM <- read_dta('ELSA_Baseline/ELSA_Baseline_summary.dta')
FEM <- read_dta('ELSA_AgeUK_valid/ELSA_AgeUK_valid_summary.dta')

@@

  # Save plot into in E-FEM_Paper/figures/
  ggsave(filename = paste0(cd, '_', gender, '.png'),
         plot = p,
         path = path,
         width = 6,
         height = 4)

  return(p)
}

@@

```{r}
# Collect all conditions (and both genders) into a list, and apply the function above to that list
cd_list <- unique(combined$Condition)
gender_list <- unique(combined$Gender)

for(cd in cd_list) {
  for(gen in gender_list) {
    plot <- visAgeUKValid(combined, cd, gen)
    print(plot)
  }
}
```
